Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Move stimuli/likelihood function figure
Fix Bessel function in Von Mises PDF

Another strategy is to assume a parametric shape for $S$ and fit the
appropriate parameters. When $h_1$ is correct, it is likely that the
function will be approximately unimodal (shapes with rotational
symmetry would be multimodal). A reasonable assumption, then, is that
the likelihood follows a ``wrapped Gaussian'', or Von Mises,
distribution:
\begin{equation}
  S(X_b, X_R) \approx h\cdot{}p(R\ \vert\ \hat{\theta}, \kappa)=\frac{h}{2\pi X_0(\kappa)}e^{\kappa\cos(R-\hat{\theta})}
\end{equation}
where $\kappa$ is the concentration parameter, $\hat{\theta}$ is the
preferred direction, and $h$ is a scale parameter. We fit these
parameters by minimizing the mean squared error between this PDF and
the computed values of $S$. To choose the sequence of rotations, we
use the same hill-climbing strategy as in the na\"ive model.\TODO{a
  better strategy would have been to compute the variance in parameter
  estimates, or something...} Figure \ref{fig:vm} shows an example of
this parametric model, prior to estimating $Z$.

>>>>

Another strategy is to assume a parametric shape for $S$ and fit the
appropriate parameters. When $h_1$ is correct, it is likely that the
function will be approximately unimodal (shapes with rotational
symmetry would be multimodal). A reasonable assumption, then, is that
the likelihood follows a ``wrapped Gaussian'', or Von Mises,
distribution:
\begin{equation}
  S(X_b, X_R) \approx h\cdot{}p(R\ \vert\ \hat{\theta}, \kappa)=\frac{h}{2\pi I_0(\kappa)}e^{\kappa\cos(R-\hat{\theta})}
\end{equation}
where $\kappa$ is the concentration parameter, $\hat{\theta}$ is the
preferred direction, $h$ is a scale parameter, and $I_0$ is the
modified Bessel function of order zero. We fit these parameters by
minimizing the mean squared error between this PDF and the computed
values of $S$. To choose the sequence of rotations, we use the same
hill-climbing strategy as in the na\"ive model.\TODO{a better strategy
  would have been to compute the variance in parameter estimates, or
  something...} Figure \ref{fig:vm} shows an example of this
parametric model, prior to estimating $Z$.
